DATA 621 Homework #3

### 2019-10-30 hw3/HW3.Rmd
cleaned some things up

## Feature Engineering
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(rpart)				        # Popular decision tree algorithm
library(rattle)					# Fancy tree plot
library(rpart.plot)				# Enhanced tree plots
library(RColorBrewer)				# Color selection for fancy tree plot
library(party)					# Alternative decision tree algorithm
library(partykit)				# Convert rpart object to BinaryTree
library(caret)
library(stringr)
library(data.table)
library(plyr);
library(dplyr)
library(randomForest)
library(memisc)
library(plotly)
library(grid)
library(fuzzyjoin)

df <- read.csv('data/crime-training-data_modified.csv')
evaluation <- read.csv("data/crime-evaluation-data_modified.csv")

>>>>

## Feature Engineering
```{r}

library(fuzzyjoin)
